Supplementary Materials to ``Statistical paradoxes in coronavirus case-counts: selection bias, measurement error, and the COVID-19 pandemic''

### 2022-03-30 write-up/covid-supplement-writeup.tex
paper is ready; tg

\paragraph{\bf Notation for Section~\ref{section:improvedcasecount} (temporal setting)}
\begin{itemize}
\item[$Y_{j,t}$] \quad Binary COVID-19 status of individual $j$ in the population at time~$t$.
\item[$I^{NR}_{j,t}$] \quad Selection indicator of individual $j$ in the population into the non-probability sample.
\item[$X_{j,t}$] \quad Feature vector for individual $j$ in the population at time~$t$ that impact self-selection into the non-probability sample.
\item[$I_{j,t}^{R}$] \quad Selection indicator of individual $j$ in the population into the probability sample.
\item[$W_{j,t}^{R}$] \quad Weight of individual $j$ in the population in the probability sample (i.e., inverse-probability of selection)
\item[$\pi (X_{j,t}; \theta)$] \quad Self-selection propensity of individual~$j$ into the non-probability sample given feature vector~$X_{j,t}$ and Probability of selection model evaluated indicator of selection of the
\item[$w (X_{j,t})$] \quad Weight of indivdual~$j$ in the population in the non-probability sample, i.e., $w(x) = 1/\pi(x; \theta)$.
\item[$\mu(X_{j,t})$] \quad The indicator of selection of the
\end{itemize}

@@

Here we present the testing propensity for four strata: (1) non-Hispanic, white female, (2) non-Hispanic, African American male, (3) Hispanic, White male.   Strata (1) presented in Figure~\ref{fig:nonh-white-female} demonstrates a small gender difference in testing propensities.  Strata (2) and (3) presented in Figures~\ref{fig:nonh-aa-male} and~\ref{fig:h-white-male} demonstrates a lower rate of testing among African Americans and Hispanic white men compared to non-Hispanic, white men respectively (approximately 2 times lower). Strata (4) presented in Figure~\ref{fig:h-other-male} demonstrates a much higher testing rate for Hispanic men who select ``Some Other Race''.

@@

Figure~\ref{fig:undercounting} is a plot of undercount based on the SEIR model.  We plot relative undercound on a cumulative basis since January due to the case counts reflecting active infections. Figure~\ref{fig:tv_air_sens} is a sensitivity analysis of the active infection rate under SEIR model with 10\% increase and decrease in the average IFR.  We see that the impact on the doubly robust estimates is minimal.

>>>>

\paragraph{\bf Notation for Section~\ref{section:improvedcasecount} (temporal setting)}
\begin{itemize}
\item[$Y_{j,t}$] \quad Binary COVID-19 status of individual $j$ in the population at time~$t$.
\item[$I^{NR}_{j,t}$] \quad Selection indicator of individual $j$ in the population into the non-probability sample.
\item[$X_{j,t}$] \quad Feature vector for individual $j$ in the population at time~$t$ that impact self-selection into the non-probability sample.
\item[$I_{j,t}^{R}$] \quad Selection indicator of individual $j$ in the population into the probability sample.
\item[$W_{j,t}^{R}$] \quad Weight of individual $j$ in the population in the probability sample (i.e., inverse-probability of selection)
\item[$\pi (X_{j,t}; \theta)$] \quad Self-selection propensity of individual~$j$ into the non-probability sample given feature vector~$X_{j,t}$ and parameter~$\theta$.
\item[$w (X_{j,t})$] \quad Weight of individual~$j$ in the population in the non-probability sample, i.e., $w(x) = 1/\pi(x; \theta)$.
\item[$\hat \mu(X_{j,t})$] \quad Model-based estimate of the active infection rate at time~$t$ for individuals with feature vector~$X_{j,t}$
\end{itemize}

@@

Here we present the testing propensity for four strata: (1) non-Hispanic, white female, (2) non-Hispanic, African American male, (3) Hispanic, White male, and (4) Hispanic male who selects `Some other Race'.   Strata (1) presented in Figure~\ref{fig:nonh-white-female} demonstrates a small gender difference in testing propensities.  Strata (2) and (3) presented in Figures~\ref{fig:nonh-aa-male} and~\ref{fig:h-white-male} demonstrates a lower rate of testing among African Americans and Hispanic white men compared to non-Hispanic, white men respectively (approximately 2 times lower). Strata (4) presented in Figure~\ref{fig:h-other-male} demonstrates a much higher testing rate for Hispanic men who select ``Some Other Race''.

@@

Figure~\ref{fig:undercounting} is a plot of undercount based on the SEIR model.  We plot relative undercount on a cumulative basis since January due to the case counts reflecting active infections. Figure~\ref{fig:tv_air_sens} is a sensitivity analysis of the active infection rate under SEIR model with 10\% increase and decrease in the average IFR.  We see that the impact on the doubly robust estimates is minimal.
